Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-06-01 draft/paper1_jenny.tex
Edit ell_color 3

	The ellipticity of the isophote contains information about the 3-D geometry 
	(e.g. \citealt{Chang2013, Mitsuda2017}) and kinematic (e.g. 
	\citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.  
	Left of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC massive 
	galaxies and highlight the median profiles for the same three \mtot{} bins used 
	in Fig \ref{fig:avg_prof}. 
	In general, the ellipticity of massive galaxy slowly increases with radius.
	One can even notice this trend by directly comparing the shape of galaxy between 
	SDSS and HSC images (e.g. Fig \ref{fig:sdss_compare}).  
	More interestingly, the ellipticity profiles clear depend on \mtot{}: 
	at ${\sim} 10$ kpc, median ellipticities from all three bins are low and similar 
	($< 0.2$); but more massive galaxies become increasingly more elongated in their
	stellar halo. 	
	For the \logms{}$>11.8$ galaxy, its median ellipticity profile becomes steeper 
	at $>10$ kpc, and the ellipticity steadily increases from $e\le 0.2$ to 
	$e{\sim} 0.4$ at 50-60 kpc.
	This is consistent with previous 2-D modeling results from \citet{Huang2013a}.
	If accreted stars dominate the stellar halos of massive galaxies, this 
	mass-dependent ellipticity profile may lead us to some insights about the 
	differences in their assembly history (e.g. average time since last merger, 
	average merger mass ratio).
	We also compare our ellipticity profiles with previous ones that are based on 
	image stacking techniques (the PSF-removed $i$-band from \citealt{Tal2011}, 
	the concentration galaxies with $11.0<$\logms{}$<11.4$ from 
	\citealt{DSouza2015}), 
	We notice that the stacked image sometimes fails to recover the ellipticity 
	profile, probably due to the uncertainties in aligning galaxies before the 
	stacking process.

    We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
    \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
    left (right) side of \ref{fig:ell_color}. 
    We also compare our results with previous work based on stacking SDSS galaxies 
    (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).

    % TODO: Move this to Paper II 
    %The ellipticity profiles of the \mtot{}-matched samples are very similar at 
    %$r<50$ kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
    %However, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
    %ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
    %profiles are very similar.  
    %This further hints that massive central galaxies in different halos but with 
    %similar ``in-situ'' mass may experience different late-time merging histories. 
    %Overall, the relative low ellipticity value and the fact that the ellipticity 
    %gradients are shallow lead us to conclude that the use of an average 
    %isophotal ellipticity is fine for this present study.

    Ellipticity profiles contain additional information about the assembly histories 
    and in future work, it would be of interest to compare our ellipticity profiles 
    with predictions from hydrodynamic simulations such as Illustris 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) or \textit{Horizon-AGN} 
    (\citealt{Dubois2014}).

    In terms of color gradients, we find shallow and negative gradients of median 
    $g-r$ and $g-i$ color profiles for both \rbcg{} and \nbcg{} galaxies. 
    {\bf Can we also look as a function of stellar mass?}
    For both \mtot{}- and \minn{}-matched samples, we find no significant difference
    in their median color profiles, which supports the assumption of using single 
    average \m2l{} value to estimate \mden{} profiles.
    The median $g-r$ color profiles are quite consistent with those based on 
    stacked SDSS images. 
    For the $g-i$ profiles, the HSC ones show steeper gradients than the SDSS ones, 
    however, it is important to point out that the SDSS $i$-band suffers from the 
    so-called ``red-halo'' effect of (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that 
    could make the SDSS color appears redder. 
    In contrast, HSC $i$-band image do not suffer from this effect (thanks to thick 
    CCDs), therefore can help provide more accurate color estimates.
%% ------------------------------------------------------------------------------------ %%

>>>>

	The ellipticity of the isophote contains information about the 3-D geometry 
	(e.g. \citealt{Chang2013, Mitsuda2017}) and kinematic (e.g. 
	\citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.  
	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC 
	massive galaxies and highlight the median profiles for the same three \mtot{} 
	bins used in Fig \ref{fig:avg_prof}. 
	In general, the ellipticity of massive galaxy slowly increases with radius.
	One can even notice this trend by directly comparing the shape of galaxy between 
	SDSS and HSC images (e.g. Fig \ref{fig:sdss_compare}).  
	More interestingly, the ellipticity profiles clear depend on \mtot{}: 
	at ${\sim} 10$ kpc, median ellipticities from all three bins are low and similar 
	($< 0.2$); but more massive galaxies become increasingly more elongated in their
	stellar halo. 	
	For the \logms{}$>11.8$ galaxy, its median ellipticity profile becomes steeper 
	at $>10$ kpc, and the ellipticity steadily increases from $e\le 0.2$ to 
	$e{\sim} 0.4$ at 50-60 kpc.
	This is consistent with previous 2-D modeling results from \citet{Huang2013a}.
	If accreted stars dominate the stellar halos of massive galaxies, this 
	mass-dependent ellipticity profile may lead us to some insights about the 
	differences in their assembly history (e.g. average time since last merger, 
	average merger mass ratio).
	We also compare our ellipticity profiles with previous ones that are based on 
	image stacking techniques (the PSF-removed $i$-band from \citealt{Tal2011}, 
	the concentration galaxies with $11.0<$\logms{}$<11.4$ from 
	\citealt{DSouza2015}), 
	We notice that the stacked image sometimes fails to recover the ellipticity 
	profile, probably due to the uncertainties in aligning galaxies before the 
	stacking process.

    As for the color profiles, it is well known that massive elliptical galaxies 
    have shallow and negative color gradient that reflects radial variation of 
    stellar population (e.g.\ \citealt{Carollo1993, LaBarbera2012}) and contains 
    information about the assembly history of stellar halos (e.g. 
    \citealt{Hirschmann2015}). 
    The right panels of Fig \ref{fig:ell_color} show the $k$-corrected $g-r$ and 
    $g-i$ color profiles and the median profiles in three \mtot{} bins. 
    As expected, all median color profiles show smooth and shallow negative 
    gradients, but we do not find evidence for mass-dependence here. 
    We also compare our results with the stacked color profiles from  
    \citealt{LaBarbera2010}\footnote{Use the median color profiles of high-mass 
    ETGs; the original profile is in unit of $R_{\mathrm{e}}$, we use a typical 
    $R_{\mathrm{e}}=8.0$ kpc to convert it into kpc unit.} and 
    \citealt{DSouza2014}.
    The median color profiles from HSC images are systematically steeper than the 
    stacked SDSS ones. 
    Considering the differences in response curves of HSC and SDSS filters, and 
    the uncertainties of color measurements, the HSC $g-r$ color profiles are 
    consistent with those based on SDSS images. 
    For the $g-i$ profiles, the HSC ones still show steeper gradients. 
    The SDSS $i$-band suffers from the so-called ``red-halo'' effect of 
    (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that could lead to redder color in 
    the low surface brightness outskirt of galaxy.
    HSC $i$-band image do not suffer from this effect (thanks to thick CCDs), 
    therefore can help provide more accurate color estimates.
    For the ones from \citet{LaBarbera2010}, uncertainty of $R_{\mathrm{e}}$ 
    measurements could also ``smooth'' the color gradients.
    The relative steeper color profiles have been observed in very nearby massive 
    ETGs individually.  
    On Fig \ref{fig:ell_color}, we also compare with the $g-r$ color profiles of 
    NGC 4472 (\citealt{Mihos2013}) and NGC 4365 (\citealt{Mihos2017})\footnote{
    Both are converted from $B-V$ colors}, and the $g-i$ profile of NGC 1399 
    (\citealt{Iodice2016}). 
    These individual profiles show similar color gradients with the HSC median ones.

    % TODO: Move to discussion
    %Ellipticity profiles contain additional information about the assembly histories 
    %and in future work, it would be of interest to compare our ellipticity profiles 
    %with predictions from hydrodynamic simulations such as Illustris 
    %\citealt{Vogelsberger2014}, \citealt{Genel2014}) or \textit{Horizon-AGN} 
    %(\citealt{Dubois2014}).

    % TODO: Move this to Paper II 
    %The ellipticity profiles of the \mtot{}-matched samples are very similar at 
    %$r<50$ kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
    %However, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
    %ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
    %profiles are very similar.  
    %This further hints that massive central galaxies in different halos but with 
    %similar ``in-situ'' mass may experience different late-time merging histories. 
    %Overall, the relative low ellipticity value and the fact that the ellipticity 
    %gradients are shallow lead us to conclude that the use of an average 
    %isophotal ellipticity is fine for this present study.
    %We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
    %\mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
    %left (right) side of \ref{fig:ell_color}. 
    %We also compare our results with previous work based on stacking SDSS galaxies 
    %(e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).

    %In terms of color gradients, we find shallow and negative gradients of median 
    %$g-r$ and $g-i$ color profiles for both \rbcg{} and \nbcg{} galaxies. 
    %For both \mtot{}- and \minn{}-matched samples, we find no significant difference
    %in their median color profiles, which supports the assumption of using single 
    %average \m2l{} value to estimate \mden{} profiles.
%% ------------------------------------------------------------------------------------ %%
